---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# synthesizer

<!-- badges: start -->
<!-- badges: end -->

synthesizer helps instructors create collaborative project teams based on student preferences and availability. The goal is to take make a manual process easier by automatically considering and balancing preferences and constraints.

This package is designed to facilitate one of the logistical challenges of collaborative, project-based, and experiential learning--creating project teams. Instead of randomly making teams, or enabling students to entirely choose their teams, synthesizer provides instructors with a streamlined way to account for student preferences. Students provide up to 4 peers they'd prefer to work with, 1 peer they'd prefer not to work with, and their availability for out-of-class meeting times based on 2 options. 

syntheizer uses integer programming to create teams that optimize the number of preferred student pairings, while ensuring students are not put with non-preferred peers and that all team members are available at the same time. This package aims to help instructors save time while also ensuring teams are created with student input.

## Installation

You can install the development version of synthesizer from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("bgormally/synthesizer")
```

## Example

This is a basic example which shows how `syn_teams` generates collaborative project teams based on the  preferences and availability from each student.

To use `syn_teams`, the data should be organized in columns as follows: each student's name; 1st preferred peer; 2nd preferred peer; 3rd preferred peer; 4th preferred peer; peer to avoid; availability. If any preferences or availability are not collected by the instructor, the columns are still required but those cells should be left blank. 

```{r example, eval=T}
library(synthesizer)
data("students")
head(students)
```

`syn_teams` generates a tibble data frame of each team, with maximized preferences while ensuring students are not with non-preferred peers and they share the same availability as their teammates.
```{r, eval=T, warning=F}
teams <- syn_teams(students = students, time_limit = 0.1)
teams
```
